SSA based global code motion of identical computations

### 2017-04-17 acmart-pacmpl-template.tex
refactor

\subsubsection{Reduce register pressure}
\label{hoist:reg-pressure}
Hoisting upwards will decrease the live-range of its use, if it is a last use (a
kill), but increase the live-range of its definition. Conversely, sinking will
decrease the live-range of the defined register but increase the live-range for
killed operands. If the live-range after code-motion is less than before it will
be moved.

Essentially, as long as there is one killed operand , code hoisting will either
decrease or preserve the register pressure. Similarly, code-sinking will either
decrease or preserve the register pressure as long as there is one operand
killed at most.

Following example explains how code motion of identical computations can reduce
the register pressure.  Consider the following example where the labels prefixed
with 'P' represent the position of instruction in a basic block (names prefixed
with 'B').

@@

\subsubsection{Hoisting expression across call}
\label{cost:across-calls}
Even hoisting scalars across calls is tricky because it can increase the number
of spills. During the frame lowering of calls, the argument registers, in
general, the caller saved registers are saved because they might be modified by
the callee and after the call they are restored. So before the call, the
register pressure is high because the number of available registers are reduced
by the number of caller saved registers. In that situation if a computation
that increases register pressure is not profitable to hoist.

@@

In our current implementation we keep as many candidates in one set as possible
(greedy approach). We split the list at a point where the legality checks fail
to hoist subset of candidates which are legal to hoist and then start finding
new hoisting point for the remaining ones.

@@

\subsection{Code generation}
Once all the legality and profitability checks are satisfied for a set of
identical instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed, and the \SSA{} form is restored by updating the
intermediate representation (IR) to reflect the changes. At the same time
MemorySSA is also updated to get up-to-date information about memory references.

>>>>

\subsubsection{Reduce register pressure}
\label{hoist:reg-pressure}
Hoisting upwards will decrease the live-range of its use, if it is a last use (a
kill), but increase the live-range of its definition. Conversely, sinking will
decrease the live-range of the defined register but increase the live-range for
killed operands. If the live-range after code-motion is less than before it will
be moved. Essentially, as long as there is one killed operand , code hoisting
will either decrease or preserve the register pressure.  Similarly, code-sinking
will either decrease or preserve the register pressure as long as there is one
operand killed at most.  Following example explains how code motion of identical
computations can reduce the register pressure.  Consider the following example
where the labels prefixed with 'P' represent the position of instruction in a
basic block (names prefixed with 'B').

@@

\subsubsection{Hoisting an expression across a call}
\label{cost:across-calls}
Even hoisting scalars across calls is tricky because it can increase the number
of spills. During the frame lowering of calls, the argument registers also known
as the caller saved registers are saved because they might be modified by the
callee and after the call they are restored. So before the call, the register
pressure is high because the number of available registers are reduced by the
number of caller saved registers. In that situation a computation that increases
register pressure is not profitable to hoist.

@@

% TODO: Rewrite the following.
In our current implementation we keep as many candidates in one set as possible
(greedy approach). We split the list at a point where the legality checks fail
to hoist subset of candidates which are legal to hoist and then start finding
new hoisting point for the remaining ones.

@@

\subsection{Code generation}
Once all the legality and profitability checks are satisfied for a set of
congruent instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed, and the \SSA{} form is restored by updating the
intermediate representation (IR) to reflect the changes. At the same time
MemorySSA is also updated to get up-to-date information about memory references.
